Single-step Hybrid Predition

### 2016-10-13 reports/loocv_example.Rmd
Add Claas' fast-loocv code

>>>>

# Claas Heuer, October 2016
#
# Fast implementation of leave-one-out cross-validation
# without reestimating variance components in a ridge
# regression framework.
# Based on Rohan's paper

library(pacman)
p_load(rrBLUP, Matrix)

LOOCVFast <- function(y, M) {

	if(!is.vector(y) | !is.numeric(y)) stop("y has to be a numeric vector")
	if(anyNA(y)) stop("no NAs allowed in y")
	if(nrow(M) != length(y)) stop("dimensions for y and M dont match")
	if(anyNA(M)) stop("no NAs allowed in M")

	# check dimensions for most efficient scheme
	if(nrow(M) < ncol(M)) {

	G <- tcrossprod(M)
	L <- t(chol(G))

	} else {

		L <- M

	}

	mod <- mixed.solve(y = y, Z = L)

	bs <- c(mod$beta, mod$u)

	vA <- mod$Vu
	vE <- mod$Ve
	lambda <- vE / vA
	D <- c(0, rep(lambda, ncol(L)))

	X <- cbind(1, L)
	Htemp <- crossprod(X)
	diag(Htemp) <- diag(Htemp) + D
	H <- X %*% solve(Htemp) %*% t(X)

	E <- (y - X %*% bs) / (1 - diag(H))
	yhat <- y - as.numeric(E)

	return(list(y = y, yhat = yhat, e = as.numeric(E), cor = cor(y, yhat)))

}
